\huge UNet-HCRF Integration for EEG Pattern Recognition

### 2024-12-12 manuscript/main.tex
minor
typo

%% notations; only define those you use frequently
\newcommand{\EE}{{\mathbb{E}}}
\newcommand{\Fb}{\mathbf{F}}
\newcommand{\hb}{\mathbf{h}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Ib}{\mathbf{I}}
\newcommand{\Lc}{\mathcal{L}}
\newcommand{\PP}{{\mathbb{P}}}
\newcommand{\QQ}{{\mathbb{Q}}}
\newcommand{\xb}{\mathbf{x}}
\newcommand{\Oc}{\mathcal{O}}
\newcommand{\one}{\mathbbm{1}}
\newcommand{\Ocal}{\mathcal{O}}
\newcommand{\RR}{{\mathbb{R}}}
\newcommand{\XX}{{\mathbb{X}}}
\newcommand{\YY}{{\mathbb{Y}}}

@@

This project introduces a novel framework that combines deep neural networks
and probabilistic graphical models (PGMs) to enhance the accuracy of EEG
pattern recognition . By employing UNet~\citep{ronneberger2015unet} for feature
extraction and integrating them with HCRF models, we aim to improve the
precision of EEG pattern recognition tagging. Furthermore, mean-field
approximation techniques are utilized for efficient inference, ensuring a
computationally efficient yet effective approach.
This integration of modern neural network architectures with HCRFs offers
a robust and promising solution for EEG pattern recognition tasks.

>>>>

%% notations; only define those you use frequently
\newcommand{\EE}{{\mathbb{E}}}
\newcommand{\Fb}{\mathbf{F}}
\newcommand{\hb}{\mathbf{h}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Ib}{\mathbf{I}}
\newcommand{\Lc}{\mathcal{L}}
\newcommand{\PP}{{\mathbb{P}}}
\newcommand{\QQ}{{\mathbb{Q}}}
\newcommand{\xb}{\mathbf{x}}
\newcommand{\Oc}{\mathcal{O}}
\newcommand{\one}{\mathbbm{1}}
\newcommand{\RR}{{\mathbb{R}}}
\newcommand{\XX}{{\mathbb{X}}}
\newcommand{\YY}{{\mathbb{Y}}}

@@

This project introduces a novel framework that combines deep neural networks
and probabilistic graphical models (PGMs) to enhance the accuracy of EEG
pattern recognition. By employing UNet~\citep{ronneberger2015unet} for feature
extraction and integrating them with HCRF models, we aim to improve the
precision of EEG pattern recognition tagging. Furthermore, mean-field
approximation techniques are utilized for efficient inference, ensuring a
computationally efficient yet effective approach.
This integration of modern neural network architectures with HCRFs offers
a robust and promising solution for EEG pattern recognition tasks.
